---
title: "Save clean data"
author: "Xuhang Li"
date: "2024-01-13"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Save clean data

In the previous steps, we have finished the QC analysis for both RNAi identity and sequencing sample quality. The wrong clones are identified and relabeled with true RNAi information and bad samples are excluded. This step is a simple wrapper function for users to save the cleaned dataset in an organized way for future analysis.

### Required packages

```{r, results = 'hide', message = FALSE, warning = FALSE}
# install if not in your environment
library(stringr)
library(dplyr)
library(tibble)
```

### Writing data

Please note that we offer the following function just for the convenience to seamlessly analyze WPS data. Please feel free to manage/organize the data in your own way!

```{r}
source('RNAi_QC_functions.R')

# we usually save the data from the same RNAi batch (plate) together 
plateID = 'met7'
libs = c('lib1','lib2','lib3','lib4','lib5','lib6')
# specify the ID (name in the treatment covariate) for control samples
controlID = 'x.vector' # in WPS, we conveniently call them 'vector'. If you use another name such as "control", change it to the actual name. 

cleanAndSave(plateID, libs, controlID)
```

Now, our clean dataset for experiment metabolite plate #7 has been saved to "/outputs/cleaned_merged_raw_data_met7.Rdata". We can proceed to biological interpretations.
